Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-10 nlp.tex
Text tweaks

Equations $3$ and $4$ are now added as a constraint to the production rule \begin{grammar} <Days> ::= NUMBER(1-31) \end{grammar}.

\subsection{Probabilistic Context-Free Grammar}
Pattern-recognition problems such as parsing date and time formats initiate from observations generated by some structured stochastic process. In other words, even if the initial higher-level production rule of the grammar is known (i.e. date, time or date-time), there could be several directions that the parser resolve to. For example, in a date string 5/6/2015, the pattern could either be M/d/yyyy or d/M/yyyy.

Probabilistic context-free grammars (PCFGs) have provided a useful method for modeling such uncertainty [cite]. Once we have created a PCFG model of a process, we can apply existing PCFG parsing algorithms to identify a variety of date-time formats. However, the parser’s success is often limited in the types of the dominant patterns that it can identify. In addition, the standard parsing techniques generally require specification of a complete observation sequence. In many contexts, we may have only a partial sequence available (e.g. an incomplete entry). Finally, we may be interested in computing the probabilities of date-time patterns that the grammar may not explicitly define. To extend the forms of evidence, inferences, and pattern distributions supported, we need a flexible and expressive representation for the distribution of structures generated by the grammar. We adopt Bayesian networks for this purpose, and define an algorithm to generate a probabilistic distribution of possible parse trees corresponding to a set of date-time patterns as opposed to individual ones.

%•	Motivate the use of context-free grammar, particularly Backus-Normal-Form
%•	Explain why we use a probabilistic version of the grammar
%•	Explain how the production rules are created based on the ICU format
%•	Extensions to the parser to account for columnar context for maximizing the probabilistic occurrence of the dominant pattern
%•	Other semantic extensions – looking at the file name, adding rules for leap year, using external dictionaries for non-English terms

>>>>

Equations $3$ and $4$ are now added as constraints to the \texttt{Days} symbol in the grammar.

\subsection{Probabilistic Context-Free Grammar}
Pattern-recognition problems such as parsing date and time formats initiate from observations generated by some structured stochastic process. In other words, even if the initial higher-level production rule of the grammar is known (i.e. date, time or date-time), there could be several directions that the parser resolves to. For example, in a date string 5/6/2015, the pattern could either be M/d/yyyy or d/M/yyyy.

Probabilistic context-free grammars (PCFGs) have provided a useful method for modeling such uncertainty [cite]. Once we have created a PCFG model of a process, we can apply existing PCFG parsing algorithms to identify a variety of date-time formats. However, the parserÕs success is often limited in the types of the dominant patterns that it can identify. In addition, the standard parsing techniques generally require specification of a complete observation sequence. In many contexts, we may have only a partial sequence available (e.g. an incomplete entry). Finally, we may be interested in computing the probabilities of date-time patterns that the grammar may not explicitly define. To extend the forms of evidence, inferences, and pattern distributions supported, we need a flexible and expressive representation for the distribution of structures generated by the grammar. We adopt Bayesian networks for this purpose, and define an algorithm to generate a probabilistic distribution of possible parse trees corresponding to a set of date-time patterns as opposed to individual ones.

%¥	Motivate the use of context-free grammar, particularly Backus-Normal-Form
%¥	Explain why we use a probabilistic version of the grammar
%¥	Explain how the production rules are created based on the ICU format
%¥	Extensions to the parser to account for columnar context for maximizing the probabilistic occurrence of the dominant pattern
%¥	Other semantic extensions Ð looking at the file name, adding rules for leap year, using external dictionaries for non-English terms
